\documentclass[../main.tex]{subfiles}

\begin{document}
\justifying
%\emergencystretch 3em
% Disable page numbers
\pagestyle{empty}
% Header
\begin{center}
    
    \textbf{\Huge Harry Pyper }\\[3pt] % Name 
    \textbf{Curriculum Vitae}\\[1pt] % CV
    M. +44 7469 738620 | {hpyper12@gmail.com} | \href{http://www.linkedin.com/in/harry--pyper12}{{Harry Pyper -- Linkedin}} | \href{https://github.com/harrypyper}{{Harry Pyper -- GitHub}}
\end{center}

%------------------------------------------------
% PROFESSIONAL SUMMARY
\textcolor{blue}{
\section*{PROFESSIONAL SUMMARY}
}
    \noindent
    \newline
    Mechanical Engineering student at Newcastle University with a focus on computational fluid dynamics and turbulent flow analysis. Experienced in Python-based simulation, high-performance computing, and numerical modelling. Seeking to apply these skills in research for fluid mechanics and machine learning.
% EDUCATION

\section*{EDUCATION}

    \noindent
    \subsection*{Mechanical Engineering BEng -- Newcastle University, Tyne and Wear, UK }(Sept 2023 -- Anticipated June 2026)
    \textbf{(Stage 1 Average -- 64.1\%) (Stage 2 Average -- 69.2\%)} 
    \begin{itemize}
        \item \textbf{Engineering project;} Performed CFD analysis using Python script to understand components of swirling turbulent flows using \textbf{Reynolds--Averaged Navier--Stokes equation} and \textbf{azimuthal averaging}.
        
        \item \textbf{Fluid Dynamics;} Developed knowledge in advanced fluid theory; mass and momentum conservation equations. Application to practical examples such as centrifugal pumps, Couette and Poiseuille flows.
        
        \item \textbf{Computational Heat and Fluid Flow;} modelling and numerical solutions of steady and unsteady state diffusion, advection diffusion, wave equation and grid generation.
        
        \item \textbf{Mechanics;} developed essential mathematical and analytical skills for static, dynamics and kinematic problems, solved tasks in labs and implemented in the crane project to analyse loads and truss forces and bridge project to evaluate and design a load bearing bridge model.
        
        \item \textbf{Thermal Engineering;} developed fundamentals to thermodynamics theory and computation over the course of several modules investigating steam and power cycles, heat exchangers, second law of thermodynamics with application to real use of power plants including effects of irreversibility and methods to improve efficiency.
        
        \item \textbf{Engineering Mathematics;} key mathematics foundations and implementation applied into physics and engineering.
        
        \item \textbf{Mechatronics Design;} groundwork of electronics including diodes, transistors and opamps and sequential logic such as Boolean Algebra and logic state machines; programming and digital skills to design systems using PID’s, controllers, motors and sensors.
        
        \item \textbf{Electronic and Magnetic Systems;} expanded knowledge and skills in analysis and calculations for AC and DC circuit theory and power conversion, applying to analysis of the Tyne and Wear Metro Network.
        \item \textbf{Properties and Behaviours of Engineering Materials;} understanding atomic structure, production methods, durability and suitability of ceramics and composites, metals and polymers
        
        \item \textbf{Engineering Skills;} developing technical skills including \textbf{Python, C/C++, MATLAB, AutoCAD (Autodesk Inventor)} and \textbf {Ansys (FLUENT, Finite Element Analysis)}; soft professional skills, problem solving, planning, organisation, teamwork and attention to detail.
    \end{itemize}
    
    \subsection*{A Levels – St Peter’s Catholic School, Surrey, UK}(Sept 2020 – Jun 2022) 
    \begin{itemize}
        \item Maths (A) and Psychology (B); BTEC -- Applied Science (Distinction Star)
    \end{itemize}
    \noindent
    \subsection*{Extended Project Qualification}(Sept 2020 – Jun 2022)
    \begin{itemize}
        \item ‘If electric cars are more energy efficient than those with internal combustion engines and if the UK has a sustainable infrastructure to support them?’ (B).
    \end{itemize}
    %\subsection*{Language \& Cultural Competency}
        \subsection*{University Wide Language Programme – Newcastle University, Tyne and Wear, UK}(Sept 2024 – current)
        \begin{itemize}
            \item Japanese Intermediate
            \item Japanese Beginners
        \end{itemize}

%------------------------------------------------
% RELEVANT WORK EXPERIENCE
\needspace{5\baselineskip}

\section*{RELEVANT WORK EXPERIENCE}

    \textbf{Tarmac LTD, Kent}(Dec 2021)
    \begin{itemize}
        \item Implemented CAD technology to measure and value work, examined cores to understand materials engineering. Introduced into the business operations of aggregate firm and job bidding process.
        \item Worked alongside skilled quantity surveyors using Excel to formulate data for future projects alongside technical spreadsheets.
    \end{itemize}

%------------------------------------------------
% WORK EXPERIENCE

\section*{WORK EXPERIENCE}

    \subsection*{The Bulls Head Inn, Surrey, UK}(Jun – Sept 2025) (Jun – Sept 2024) (Jun – Oct 2022) (Nov 2018 – Mar 2020)
    \begin{itemize}[noitemsep]
        \item Worked within a fast--paced kitchen team with a high level of communication. Adaptability under high pressure maintaining quality results.
        \item Developed and tested dishes, guided by highly skilled experienced chefs.
 %       \item Implemented elevated organisation and planning to prepare and streamline for the future and for others.
    \end{itemize}
    \subsection*{Wild Blue, British Columbia, Canada}(Feb -- May 2023)
    \begin{itemize}[noitemsep, topsep=0pt]
        \item As a commis chef on the raw bar and garde manger performing intricate tasks under time sensitive situations.
        \item \textbf{Wild Blue was awarded \#4 best new restaurant in Canada 2023 and \#66 Best restaurant in Canada 2023.}
        \item Coordinated prep and execution of cold dishes such as salads, sashimi, oysters, cold crab, cold lobster and caviar.
        \item Advancing knowledge of food, the importance of the work environment, effective and efficient communication.
    \end{itemize}
    \subsection*{Blacks Pub, British Columbia, Canada}(Nov 2022 – May 2023)
    \begin{itemize}
        \item Part time as a line cook preparing and on the line during service. The kitchen serves American and Italian cuisine allowing development of numerous cooking techniques.
        \item Improving ability to co--ordinate with the team in an intense environment with complex dishes.
    \end{itemize}
 %   \subsection*{Roundhouse Lodge, British Columbia, Canada}(Nov 2022 – Feb 2023)
 %   \begin{itemize}
 %       \item As a prep chef, organised the equipment and stock levels at stations, maintained food stock levels in the kitchen, adapted dishes to dietary requirements of customers during a fast--paced service.
 %   \end{itemize}
    
%------------------------------------------------
% VOLUNTEERING EXPERIENCE

\section*{VOLUNTEERING EXPERIENCE}
   
    \subsection*{Wey and Arun Canal Trust, Surrey, UK}(May 2021 – Oct 2022)
        \begin{itemize}
            \item Part of a team rebuilding a canal basin and foot/road bridge. Used an electronic theodolite, installed rebar for concrete frames, redirected telephone cables and laid bricks. Interpreted CAD drawings for practical use.
        \end{itemize}

\section*{ADDITIONAL EDUCATION}

        \subsection*{Orchards Cooking School}(Aug 2021)
        \begin{itemize}
            \item Prepared cooked breakfasts, afternoon teas and five course dinner parties. Participated in a cake baking competition and a wine tasting course.
        \end{itemize}
%    \subsection*{Control of Substances Hazardous to Health (COSHH) Certificate}(May 2022)
        \begin{itemize}
            \item Regulations, hazardous substances, identifying hazardous symbols, safety data sheets, COSHH risk assessments.
        \end{itemize}
%------------------------------------------------
% Service and Professional Development Section

\section*{ACHIEVEMENTS}

    \subsection*{Gold Duke of Edinburgh}(Sept 2020 – Jun 2022)
    \begin{itemize}
        \item Expedition in North Yorkshire Moors with 4 others, one year volunteered at the Wey and Arun Canal Trust, one year of Martial Arts, one year of learning drums and week residential at Orchards Cooking School.
        \end{itemize}
    \subsection*{Solo Travels}(Summer 2023)
    \begin{itemize}
        \item Hiking and canoeing independently in remote areas of Canada.
    \end{itemize}

\section*{ADDITIONAL SKILLS}

    \begin{itemize}
        \item IT competency: \textbf {LaTeX}, Microsoft Office: Outlook, Word, PowerPoint, Excel.
        \item Driving licence
    \end{itemize}
% End document
\end{document}
%--------------------------------------------------------------------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------------------------------------------------------------------